On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2021-03-25 paper/cav_determinisim_main.tex
added changes to cuda, footnote author contrib, email addresses

\begin{itemize}[leftmargin=*]
    \item System memory: \texttt{memtest86}~\cite{MemTest86} full suite of tests ran, all passed.
    \item Graphical memory: \texttt{cuda\_memtest}~\cite{cuda_memtest}, \cite{shi2009testing}.
\end{itemize}

@@

A summary of the main the results are shown in Table~\ref{TableOfExperiments}.  In the column $\max\sigma$ (unrestricted) the value reported is the maximum deviation across all resource utilisation levels, i.e.\ the worst case for a given scenario.  
%
From these results it is clear that scenarios with only pedestrian actors (Tests 5 \& 6) display results within tolerance over all resource utilisation levels with or without a collision where $\max\sigma$ is $5.6\times10^{-13}$ or $0.56\si{\pico\metre}$. 
%
However, all other scenarios involving vehicles or a mixture of actor types do not meet the required tolerance, with some deviation in actor path as large as $59$cm.
%
\todo[inline,color=green!40]{GC Edit: From these  results it is clear that scenarios with only pedestrian actors (tests 5-6) display results within the permissible tolerance over all resource utilisation levels with or without a collision where $\max\sigma$ is $5.6\times10^{-13}$ or $0.56\si{\pico\metre}$. However, all other scenarios involving vehicles or a mixture of actor types breach the permissible tolerance that has been set, with some deviation in actor path as large as $59$cm. }
%
Clearly, such a large deviation cannot be acceptable for simulation to be considered a credible verification tool.

>>>>

\begin{itemize}[leftmargin=*]
    \item System memory: \texttt{memtest86}~\cite{MemTest86} full suite of tests ran, all passed.
    \item Graphical memory: \texttt{cuda\_memtest}~\cite{cuda_memtest}, no failures on all 11 tests~\cite{shi2009testing}.
\end{itemize}

@@

A summary of the main results are shown in Table~\ref{TableOfExperiments}.  In the column $\max\sigma$ (unrestricted) the value reported is the maximum deviation across all resource utilisation levels, i.e.\ the worst case for a given scenario.  
%
From these results it is clear that scenarios with only pedestrian actors (Tests 5 \& 6) display results within tolerance over all resource utilisation levels with or without a collision where $\max\sigma$ is $5.6\times10^{-13}$ or $0.56\si{\pico\metre}$. 
%
However, all other scenarios involving vehicles or a mixture of actor types do not meet the required tolerance, with some deviation in actor path as large as $59$cm.
%
\todo[inline,color=green!40]{GC Edit: From these  results it is clear that scenarios with only pedestrian actors (tests 5-6) display results within the permissible tolerance over all resource utilisation levels with or without a collision where $\max\sigma$ is $5.6\times10^{-13}$ or $0.56\si{\pico\metre}$. However, all other scenarios involving vehicles or a mixture of actor types breach the permissible tolerance that has been set, with some deviation in actor path as large as $59$cm. }
%
Clearly, such a large deviation cannot be acceptable for simulation to be considered a credible verification tool.

### 2021-03-25 paper_arxiv/arxiv_cav_determinisim_main.tex
the main the
added changes to cuda, footnote author contrib, email addresses

\authorrunning{G. Chance, A. Ghobrial et al.}
\institute{University of Bristol, Bristol, UK \and University of the West of England, Bristol, UK \and Bristol Robotics Laboratory, Bristol, UK}
\tocauthor{Authors' Instructions}
\maketitle

>>>>

\authorrunning{G. Chance, A. Ghobrial et al.}
\institute{University of Bristol, Bristol, UK \and University of the West of England, Bristol, UK \and Bristol Robotics Laboratory, Bristol, UK}
\tocauthor{Authors' Instructions}

\maketitle
\let\thefootnote\relax\footnotetext{\textit{Greg Chance and Abanoub Ghobrial contributed equally to this paper and are both corresponding authors.}
Greg Chance (e-mail: greg.chance@bristol.ac.uk), 
Abanoub Ghobrial (e-mail: abanoub.ghobrial@bristol.ac.uk), 
Kevin McAreavey (e-mail: kevin.mcareavey@bristol.ac.uk), 
and 
Kerstin Eder (e-mail: kerstin.eder@bristol.ac.uk) 
are with the Trustworthy Systems Lab, Department of Computer Science, University of Bristol, Merchant Ventures Building, Woodland Road,  Bristol, BS8 1UQ, United Kingdom. 
%
S\'everin Lemaignan (e-mail: severin.lemaignan@brl.ac.uk)
and
Tony Pipe (e-mail: tony.pipe@brl.ac.uk), 
are with the Bristol Robotics Lab, T Block, University of the West of England,Frenchay, Coldharbour Ln, Bristol, BS34 8QZ, United Kingdom. 
}.
